R Notebook

### 2022-06-02 Code/Simulation.Rmd
sketch for arma(1,1) working copula

>>>>

```{r ARMA(1,1) D}
test_copula_D <- function(x, pdist, qdist, B, ...) {

    ## Get observed statistic
    n <- length(x) 
    stat  <- ks.test(x, dist, mean = mean, sd = sd)$statistic

    ## transform the data to standard normal scale and fit arma(1,1)
    zx <- qnorm(rank(x) / (n + 1))
    fit <- tseries::arma(zx, include.intercept = FALSE)

    ## Perform parametric bootstrap to get an empirical distribution of stat
    stat.b <- double(n)

    for (i in 1:B) {
        ## 1. The marginal distribution is the fitted dist
        ## 2. There is arma(1,1) dependence on the normal scale
        zx.b <- arima.sim(n, ...) # simulate from fit
        u <- pnorm(zx.b)
        # Transform bootstrap sample and fit the parameters
        x.b <- qdist(u, ...) # mean = mean, sd = sd)

        # Gather bootstrap sample's test statistic
        stat.b[i] <- ks.test(x.b, pdist, mean = mean, sd = sd)$statistic # fix
    }

    return(p.value)
}
```
